---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# stabilty_simmulation

<!-- badges: start -->
<!-- badges: end -->

In this repository I have simulations of fluctuation in community abundance to
understand the impacts of monitoring schemes on the accuracy of stability metrics. 

The simulation was done by:

- Simulating sine wave fluctuation of abundance at species level in a community for a fixed time. 
- Setting the mean abundance of each species in the community following a log-normal distribution 
- Sine wave was simulated using two parameter frequency and amplitude. 
- Different combination of frequency and amplitude was defined at the community level trying to emulate differences in pace-of-life of different taxonomic groups, with a positive relationship between frequency and amplitude. Fast taxon can fluctuate in high frequency and also can have high amplitude since. These relates to the short lifespan and high reproductive output. 
- The variability in frequency and amplitude among species in a community was also simulated. 


The simulation was run using 360 combination of parameter with 100 repetition. Then in the `output/comm_sim` folder you can find 36000 files, one for each simulation run. In the `output/stat_df.rds` file you find the community stability and asynchrony statistic for each simulation run.

## Shiny app
You can check this shiny app to play with different parameters and see the results for one community:
https://avrodrigues.shinyapps.io/stab_sync/

## Repo structure
```{r, echo= FALSE}
fs::dir_tree(path = ".", recurse = 1, all = F)
```






